Four reasons your build is slow

### 2019-01-17 paper.tex
work on section 'unnecessarily sequential'

A makefile which is too sequential will suffer from an excessively large span.
% not sure what to say here

To diagnose this problem using our tool, the user can calculate the span of the original build
graph and then let the tool build a new graph using strace data and calculate the span of the
new graph.  If the span of the new graph is less than the span of the original graph then the
original graph was unnecessarily sequential.

The way to fix a graph like this is for the makefile writer to re-write the makefile to
remove the false-dependencies discovered by the tool.

Example: todo

@@

>>>>

@@

A makefile which is too sequential will have a longer than necessary span.  In the previous
section we talked about projects having a long span because it was dominated by a single
long running shell command.  Another possiblility is the span being made up of many shell
commands; none of which dominate.  In the previous section we talked about zstd, and if we
rewrite the makefiles so the long running commands are made up of many sequential compilation
and then linking commands we end up with a build that has the same work and span as the original.

To diagnose this problem using our tool, the user can once again calculate the span of the build
graph and look at what targets and shell calls constitute the span.  In this case the span is
made up of many short running compilation jobs.  To check if these compilation jobs may run in
parallel, our tool will take the original graph, the collected strace data, and build a new graph
as described in section \ref{sec:revisegraphs}.  The span of the new graph can then be compared
to the span of the old graph; if the span of the new graph is less than the span of the old graph,
then the original graph was unnecessarily sequential.  The allow this build to run faster in the
future, the developer can rewrite the makefile to reflect the organization of the build in
the new graph.

In the case of zstd, when built with strace; the calculated work for the original graph is 133
seconds and the span is 45 seconds; which means a parallelism of 2.95.  When this graph is
rebuilt using strace data and the span is recalculated, it is 8 seconds, which matches with the
predictions and observations from section \ref{sec:expensive}.
